### 2019-07-07 thesis.tex
Version before serious modification in subsection 4.1.3
Version before adding a more deep explanation on the contribution of the noneigenmode term to the wave kinetic equation.

In a recent paper \cite{YZKS16}, it was presented the first rigorous
theory that, starting from first principles, incorporates collisional
effects into the already well established weak turbulence formalism.
The authors used the same standard weak turbulence perturbative method
but, instead of keeping only the collective eigenmodes in the linear
and nonlinear wave-particle interactions, they also kept the effects
of the non-collective fluctuations emitted by thermal particles. The
outcome is a complete first principles nonlinear description of the
propagation of electrostatic oscillations in the presence of both wave
and particle collisional dissipation, and a hitherto unknown process.
This new effect depicts the emission of electrostatic radiation in the
eigenmode frequency range, which is caused by particle scattering. 
Since this is a form of braking radiation, the authors named it as
\emph{electrostatic bremsstrahlung}.

@@

The plasma is a collection of ions, electrons and neutral particles that has
its dynamics dominated by the electric and magnetic fields, generated by the
electrically charged particles and the electric currents related to their
motion, respectively. Due to the long-range nature of these self-generated
fields, one particle affects the movement of several other particles, which
will interact with other particles, and so on. This \emph{collective behavior}
\footnote{A detailed description of all the processes and conditions that
  characterize the collective behavior in plasmas, can be accessed in the
  following introductory books \cite{bitt,gurnett2017,chen,DavidsonNonNeutral}.}
is what characterizes an ionized gas as a plasma, and is also the reason
behind the complexity of the plasma dynamics. This complexity comes in the
form of a myriad of self-consistent oscillatory processes, where the electric
and magnetic fields affect - and are affected by - the position and motion of
the charges, and how they vary in time \cite{chen}.

A complete description of such a complicated dynamics would depend on determining
the position and momentum of each particle, and their respective microscopic
electric and magnetic fields, in a time instant. This strategy is not practical
and in most of the cases not feasible for many-body systems, like the plasma.  
However, this microscopic description can be dealt through a hierarchy of
approximations, leading to the three main theories of plasma physics: kinetic,
multi-fluid, and magnetohydrodynamics (MHD). The use of each one of these
formulations will depend on the phenomenon that needs to be described,

@@

Proceeding under the perturbative approach, we assume small
fluctuations and write the velocity distribution function
and the electric field as a sum of an equilibrium zero-order
term and a small first-order fluctuation
\begin{equation}
  \label{pert-nl}
  \begin{split}
      f_a({\bf r}, {\bf v},t)&=F_a({\bf v})+\delta f_a({\bf r}, {\bf v},t)\\
  {\bf E}({\bf r},t)&=\delta {\bf E}({\bf r},t),
  \end{split}
\end{equation}
where the zero-order electric field is assumed to be zero and
$F_a$ is the equilibrium velocity distribution.

@@

It is interesting to mention that at this stage, Eqs. \eqref{form_par}
and \eqref{flut} are precisely the same as those leading to the
quasilinear approximation.
% LFZ180216: Sugiro "are precisely the same as those leading to the
% quasilinear approximation."
% Sabrina: OK
Thus, at this point, one must choose whether the quasilinear approach
is enough or if a nonlinear formulation is necessary. In the first case
all terms proportional to $\delta {\bf E} \delta f_a$ are neglected in
the equation for the fluctuations\footnote{See subsection 3.1.2 of
  \cite{Tigik2015}.}. We shall keep these terms and proceed with the
nonlinear approach.

Now we assume the fluctuations may be decomposed in terms of the
Fourier-Laplace transformation over the fast time-scale of the
fluctuations, while amplitudes of the spectra vary in a slow
time-scale
\begin{equation}
\begin{split}
  \delta f_a({\bf r}, {\bf v},t)
  &=\int d^3k \int_L d \omega\
  \delta f^a_{{\bf k}, \omega}({\bf v}, t)e^{i({\bf k \cdot r}-\omega t)},\\
  \delta f^a_{{\bf k}, \omega}({\bf v}, t)
  &=\frac{1}{(2 \pi)^4} \int d^3 r \int_0^{\infty} dt\
  \delta f_a({\bf r}, {\bf v},t) e^{-i({\bf k \cdot r} - \omega t)},\\
  \delta {\bf E}({\bf r},t)
  &=\int d^3 k \int_L d \omega\ \delta {\bf E}_{{\bf k},\omega}(t)
  e^{i({\bf k \cdot r}-\omega t)},\\
  \delta {\bf E}_{{\bf k},\omega}(t)
  &=\frac{1}{(2 \pi)^4}\int d^3 r \int_0^{\infty} dt\
  \delta {\bf E}({\bf r},t) e^{-i({\bf k \cdot r} - \omega t)},
\end{split}
\end{equation}
% LFZ180216: Na última equação o denominador deve ser (2\pi)^4 ao invés de
% 2\pi^4, não?
% Sabrina: OK
where the integration path is taken along $L$, stretching from
$\omega = -\infty +i\sigma$ to $\omega=\infty+i\sigma$, in which
$\sigma >0$ and $\sigma \rightarrow 0$. We should emphasize that
we assume slow and adiabatic time-dependence for the spectral
amplitudes $\delta f^a_{{\bf k},\omega}({\bf v},t)$ and
$\delta {\bf E}(t)_{{\bf k}, \omega}$ in the above transformation.

>>>>

In a recent paper \cite{YZKS16}, it was presented the first rigorous
theory that, starting from first principles, incorporates collisional
effects into the already well established weak turbulence formalism.
The authors used the same standard weak turbulence perturbative method
but, instead of keeping only the collective eigenmodes in the linear
and nonlinear wave-particle interactions, they also kept the effects
of the non-collective fluctuations emitted by thermal particles. The
outcome is a complete nonlinear description, from first principles, of
the propagation of electrostatic oscillations in the presence of both
wave and particle collisional dissipation and a new equation describing
a hitherto unknown process. This new effect depicts the emission of
electrostatic radiation, in the eigenmode frequency range, caused by
particle scattering. Since this is a form of braking radiation, the
authors named it as \emph{electrostatic bremsstrahlung}.

@@

The plasma is a collection of ions, electrons and neutral particles that has
its dynamics dominated by the electric and magnetic fields, generated by the
electrically charged particles and the electric currents related to their
motion, respectively. Due to the long-range nature of these self-generated
fields, one particle affects the movement of several other particles, which
will interact with other particles, and so on. This \emph{collective behavior}
\footnote{A detailed exposition of all the processes and conditions that
  characterize the collective behavior in plasmas, can be accessed in the
  following introductory books \cite{bitt,gurnett2017,chen,DavidsonNonNeutral}.}
is what characterizes an ionized gas as a plasma, and is also the reason
behind the complexity of the plasma dynamics. This complexity comes in the
form of a myriad of self-consistent oscillatory processes, where the electric
and magnetic fields affect - and are affected by - the position and motion of
the charges, and how they vary in time \cite{chen}.

A complete description of such a complicated dynamics would depend on determining
the position and momentum of each particle, and their respective microscopic
electric and magnetic fields, in a given instant in time. This strategy is not
practical and in most of the cases not feasible for many-body systems, like the
plasma. However, this microscopic description can be dealt through a hierarchy of
approximations, leading to the three main theories of plasma physics: kinetic,
multi-fluid, and magnetohydrodynamics (MHD). The use of each one of these
formulations will depend on the phenomenon that needs to be described.

@@

Proceeding under the perturbative approach, we assume small
fluctuations and write the velocity distribution function
and the electric field as a sum of an equilibrium zero-order
term and a small first-order fluctuation
\begin{equation}
  \label{pert-nl}
  \begin{split}
      f_a({\bf r}, {\bf v},t)&=F_a({\bf v})+\delta f_a({\bf r}, {\bf v},t)\\
  {\bf E}({\bf r},t)&=\delta {\bf E}({\bf r},t),
  \end{split}
\end{equation}
where the zero-order electric field is assumed to be zero and
$F_a$ is the equilibrium velocity distribution function.

@@

It is interesting to mention that at this stage, Eqs. \eqref{form_par}
and \eqref{flut} are precisely the same as those leading to the
quasilinear approximation.
% LFZ180216: Sugiro "are precisely the same as those leading to the
% quasilinear approximation."
% Sabrina: OK
Thus, at this point, one must choose whether the quasilinear approach
is enough, or if a nonlinear formulation is necessary. In the first case
all terms proportional to $\delta {\bf E} \delta f_a$ are neglected in
the equation for the fluctuations\footnote{See subsection 3.1.2 of
  \cite{Tigik2015}.}. We shall keep these terms and proceed with the
nonlinear approach.

Now, we assume the fluctuations may be decomposed in terms of the
Fourier-Laplace transformation over the fast time-scale of the
fluctuations, while amplitudes of the spectra vary in a slow
time-scale
\begin{equation}
\begin{split}
  \delta f_a({\bf r}, {\bf v},t)
  &=\int d^3k \int_L d \omega\
  \delta f^a_{{\bf k}, \omega}({\bf v}, t)e^{i({\bf k \cdot r}-\omega t)},\\
  \delta f^a_{{\bf k}, \omega}({\bf v}, t)
  &=\frac{1}{(2 \pi)^4} \int d^3 r \int_0^{\infty} dt\
  \delta f_a({\bf r}, {\bf v},t) e^{-i({\bf k \cdot r} - \omega t)},\\
  \delta {\bf E}({\bf r},t)
  &=\int d^3 k \int_L d \omega\ \delta {\bf E}_{{\bf k},\omega}(t)
  e^{i({\bf k \cdot r}-\omega t)},\\
  \delta {\bf E}_{{\bf k},\omega}(t)
  &=\frac{1}{(2 \pi)^4}\int d^3 r \int_0^{\infty} dt\
  \delta {\bf E}({\bf r},t) e^{-i({\bf k \cdot r} - \omega t)},
\end{split}
\end{equation}
% LFZ180216: Na última equação o denominador deve ser (2\pi)^4 ao invés de
% 2\pi^4, não?
% Sabrina: OK
where the integration path is taken along $L$, stretching from
$\omega = -\infty +i\sigma$ to $\omega=\infty+i\sigma$, in which
$\sigma >0$ and $\sigma \rightarrow 0$. We should emphasize that
we assume slow and adiabatic time-dependence for the spectral
amplitudes $\delta f^a_{{\bf k},\omega}({\bf v},t)$ and
$\delta {\bf E}(t)_{{\bf k}, \omega}$ in the above transformation.
